CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-08 paper.Rmd
Working on example

# Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

# Run the PFUAggDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))
```

>>>>

# Run the PFUDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

# Run the PFUAggDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))
```
